---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# The analysis of the activity data
2024/11/06

By Satoshi Ohnishi

### 1. Read the activity data 
Load the necessary libraries and read the activity data.

```{r simulation, echo=TRUE}

library(dplyr)
library(ggplot2)

# read activity.csv
activity <- read.csv("activity.csv")
head(activity)
```


### 2. Caliculate total number of steps taken per day
Now, Let us calculate the total number of steps taken per day.
```{r, echo=TRUE}
total_steps <- aggregate(steps ~ date, data = activity, sum)
total_steps
```

### 3. make histogram of the total number of steps taken each day
How distributed the total number of steps taken each day is?

Let us make a histogram of the total number of steps taken each day.

```{r, echo=TRUE}
hist(total_steps$steps,
     main = "Total number of steps taken each day", 
     xlab = "Number of steps", 
     ylab = "Frequency", col = "skyblue")
```

### 4. Calculate the mean and median of the total number of steps taken per day
What is the mean and median of the total number of steps taken per day?

```{r, echo=TRUE}
#Calculate the mean and median of the total number of steps taken per day
mean_steps <- mean(total_steps$steps, na.rm = TRUE)
median_steps <- median(total_steps$steps, na.rm = TRUE)

# print mean
print(mean_steps)
# print median
print(median_steps)
```


### 5. Time series plot of the average number of steps taken
Now, let us look at the time series plot of the average number of steps taken, averaged across all days.

```{r, echo=TRUE}
# Make time series plot of the 5-minute interval and the average number of steps taken, averaged across all days
ggplot(data = activity, aes(x = interval, y = steps)) +
  geom_line(stat = "summary", fun.y = "mean", col = "darkgreen") +
  labs(title = "Time series plot of the average number of steps taken",
       x = "Interval",
       y = "Average number of steps taken")


```


### 6. The maximum number of steps taken in 5-minute interval

Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r, echo=TRUE}
# Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
max_interval <- activity %>% 
  group_by(interval) %>% 
  summarise(mean_steps = mean(steps, na.rm = TRUE)) %>% 
  filter(mean_steps == max(mean_steps))

print(max_interval)
```


### 7. Imputing missing values and make histogram of the total number of steps taken each day after missing values are filled in
I think that missing values should be filled in with the 0 value.

Because if fill in with the mean or median value, the distribution of the data becomes bigger than the original data.

The monitors may be sleeping or 

Therefore, I will fill in the missing values with 0.


```{r, echo=TRUE}
# Fill in the missing values with 0
activity_imputed <- activity[is.na(activity$steps), "steps"] <- 0
# Calculate the total number of steps taken per day
total_steps_imputed <- aggregate(steps ~ date, data = activity, sum)
  
hist(total_steps_imputed$steps,
     main = "Total number of steps taken each day", 
     xlab = "Number of steps", 
     ylab = "Frequency", col = "orange")

# Calculate the mean and median of the total number of steps taken per day
mean_steps_imputed <- mean(total_steps_imputed$steps, na.rm = TRUE)
median_steps_imputed <- median(total_steps_imputed$steps, na.rm = TRUE)
print(mean_steps_imputed)
print(median_steps_imputed)
```


### 8. Are there differences in activity patterns between weekdays and weekends?
How different are the activity patterns between weekdays and weekends?

Let us make a panel plot containing a time series plot of the 5-minute interval and the average number of steps taken, averaged across all weekday days or weekend days.

```{r, echo=TRUE}
# Create new column "weekday" sunday and saturday is weekend, other days are weekday
activity$date <- as.Date(activity$date)
activity$weekday <- weekdays(activity$date)
activity$weekday <- ifelse(activity$weekday == "土曜日" | activity$weekday == "日曜日", "weekend", "weekday")

# Make 2 panel plot containing a time series plot of the 5-minute interval and the average number of steps taken, averaged across all weekday days or weekend days
# weekday color is red, weekend color is blue
ggplot(data = activity, aes(x = interval, y = steps)) +
  geom_line(stat = "summary", fun.y = "mean", color = "orangered") +
  facet_wrap(~ weekday, ncol = 1, nrow = 2) +
  labs(title = "Average number of steps taken by 5-minute interval",
       x = "Interval",
       y = "Average number of steps") +
  theme_minimal()
```

### 9. Conclusion

In the weekday, the number of steps taken is high in the morning.

In the weekend, the number of steps taken is higher in afternoon than in than weekday.

I think that the handling of missing values is important.

In this analysis, I filled in the missing values with 0.

But it may be better to fill in with the mean or median value.

I believe that the handling of missing values changes the distribution of the data and results and conclusions may change.



## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
